<<<<<<< HEAD
---
title: "PEC2"
author: "Alba Machado López - Javier Pueyo Aina"
date: "08/5/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Sección 1.

### Ejercicio 1

```{r}

```

```{r}

```


### Ejercicio 2

```{r}

```

```{r}

```

### Ejercicio 3

```{r}

```

```{r}

```

### Ejercicio 4

```{r}

```

```{r}

```

### Ejercicio 5

```{r}

```

```{r}

```

### Ejercicio 6

```{r}

```

```{r}

```

### Ejercicio 7

```{r}

```

```{r}

```

### Ejercicio 8

```{r}

```

```{r}

```


# Sección 2. Análisis cluster con R


```{r}

```


```{r}

```





=======
---
title: "PEC2"
author: "Alba Machado López - Javier Pueyo Aina"
date: "08/5/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Sección 1.

### Ejercicio 1

```{r}

```

```{r}

```


### Ejercicio 2

```{r}

```

```{r}

```

### Ejercicio 3

```{r}

```

```{r}

```

### Ejercicio 4

```{r}

```

```{r}

```

### Ejercicio 5

```{r}

```

```{r}

```

### Ejercicio 6

```{r}

```

```{r}

```

### Ejercicio 7

```{r}

```

```{r}

```

### Ejercicio 8

```{r}

```

```{r}

```


# Sección 2. Análisis cluster con R


```{r}

```


```{r}

```





>>>>>>> 28dc7779fc04af5b414b2a660233a75835bf8a67
